\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{FitEval Privacy Policy}
\fancyhead[R]{Page \thepage\ of \pageref{LastPage}}
\fancyfoot[C]{\thepage}

% Defining document structure
\begin{document}

% Title section
\begin{center}
    \textbf{\Large Privacy Policy for FitEval - BMI Calculator App} \\
    \vspace{0.5cm}
    \textit{Last Updated: June 20, 2025} \\
    \vspace{0.5cm}
\end{center}

% Introducing main content
\section*{Introduction}
Providing clarity on data handling practices for FitEval users.

FitEval ("we," "us," or "our") is committed to protecting your privacy. This Privacy Policy explains how we handle data in the FitEval BMI Calculator App, built using Flutter. By using FitEval, you agree to the practices described herein.

% Detailing data collection
\section*{Data We Collect}
Describing data collection methods used within the app.

FitEval collects the following data locally on your device to provide its services:
\begin{itemize}
    \item Age
    \item Gender
    \item Height (in CM or Inches)
    \item Weight
    \item Calculated BMI results
\end{itemize}
This data is stored locally on your device and is not transmitted to any server or third party.

% Explaining data usage
\section*{How We Use Your Data}
Outlining purposes for collected data.

We use the data collected to:
\begin{itemize}
    \item Calculate your BMI in real-time
    \item Save your BMI results for future reference
    \item Provide classification (Underweight, Normal, Overweight, Obese)
\end{itemize}
No data is used for advertising, analytics, or any purpose beyond the app's functionality.

% Addressing data storage
\section*{Data Storage}
Detailing storage practices for user data.

All data is stored locally on your device using Flutter's secure storage mechanisms. We do not upload, sync, or store your data on remote servers. You can clear this data by uninstalling the app or manually deleting saved results within the app.

% Discussing data sharing
\section*{Data Sharing}
Explaining absence of data sharing.

We do not share, sell, or transfer your data to third parties. Since all data remains local, it is not accessible to us or any external entity.

% Covering user rights
\section*{Your Rights}
Highlighting user control over data.

You have the right to:
\begin{itemize}
    \item Access and view your saved BMI results within the app
    \item Delete saved data by clearing it manually or uninstalling the app
    \item Refrain from providing any data, though this may limit app functionality
\end{itemize}

% Addressing security measures
\section*{Security}
Describing efforts to protect user data.

We implement reasonable security measures to protect data stored locally on your device. However, no method is 100\% secure, and you are responsible for the security of your device.

% Noting changes to policy
\section*{Changes to This Policy}
Indicating potential updates to privacy practices.

We may update this Privacy Policy periodically. Changes will be effective upon posting the revised policy within the app. We encourage you to review it regularly.

% Providing contact information
\section*{Contact Us}
Offering support for privacy concerns.

For questions or concerns, please contact us at:
\begin{itemize}
    \item Email: support@fitevalapp.com
\end{itemize}

\end{document}